Liveness-Based Garbage Collection for Lazy Languages

### 2015-06-06 paper/paper.tex
Updated the example program

\begin{figure*}[t!]
  \begin{tabular}{cc}
    \begin{minipage}{.40\textwidth}
        \small
        \renewcommand{\arraystretch}{1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\
(\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF\
$\psi_1\!\!:\,$ \px
            \UNL{4} \hspace*{.27cm} $\pi_3\!\!:\,
            $(\LET\ \pv\ $\leftarrow 0$ \IN
            \UNL{5} \hspace*{.32cm} $\pi_4\!\!:\,
(\SRETURN~\psi_2:\pv)$
            \UNL{4} \hspace*{.29cm}    $\pi_5\!\!:\, $(\LET~\pu\
$\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{.34cm}   $\pi_6\!\!:\, $(\LET~\py\
$\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{.34cm} $\pi_7\!\!:\,
            $(\LET~\pz\ $\leftarrow$ (1~+~\py) \IN
            \UNL{7} \hspace*{.34cm} $\pi_8\!\!:\,
(\SRETURN~\psi_3:\pz)$)))))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
	  \UNL{1} $(\DEFINE\ (\main)$
          \UNL{2} \!\!$\pi_9\!\!:\, (\LET\  \pa\  \leftarrow$ \ldots
\IN
	  \UNL{3}   \hspace*{.05cm}$\pi_{10}\!\!:\,      $ (\LET\ \pb\
$\leftarrow$  \ldots \IN
          \UNL{4}   \hspace*{.15cm}    $\pi_{11}\!\!:\,
          $(\LET\ \pw\  $\leftarrow$  (\length\ \pb) \IN
          \UNL{5}  \hspace*{.25cm}  $\pi_{12}\!\!:\,
(\SRETURN~\psi_4:\pw)))))$
\end{uprogram}}
        %%}
    \end{minipage}

@@

        \small
\begin{eqnarray*}
        \mathcal{L}(e_{\length},\sigma,\Lfonly) &=&
              [\;ep_1 \mapsto \lbrace \px.\cbar \sigma,
\xl.\cbar\sigma\rbrace ,~ep_2 \mapsto \lbrace \cred{
\pv.\sigma}  \rbrace,\\
 &&          \;\;  ep_3 \mapsto \lbrace \pz.\sigma,
                \py.\cbar\sigma,
\pu.\Lf{\length}{\mbox{1}}{\cbar\sigma},\\
&&            \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; 
\xl.\{ \acdr\Lf{\length}{\mbox{1}}{\cbar\sigma} \cup 
%%\;\;\;\;\;\;\; \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\\
\cred{\cbar\Lf{\length}{1}{\cbar\sigma}}\}\}
             \rbrack \\
            \cal{P_{\mbox{\tiny \length}}} &=&
                [\;\pi_1 \mapsto \lbrace ep_1, ep_2, ep_3 \rbrace,  \
                 \pi_2 \mapsto \lbrace ep_1, ep_2, ep_3
                  \rbrace, \\
&&\;\;  \pi_3 \mapsto \lbrace ep_2
                  \rbrace ,  \pi_4 \mapsto \lbrace ep_2
                  \rbrace, \pi_5 \mapsto \lbrace  ep_3 \rbrace, \\
 &&  \;\;                        \pi_6 \mapsto \lbrace ep_3 \rbrace,
\pi_7 \mapsto
                   \lbrace ep_3\rbrace, \pi_8 \mapsto \lbrace ep_3
\rbrace~\rbrack\\
              \mathcal{L}(e_{\main},\sigma,\Lfonly) &=&
                [\;
                  ep_4 \mapsto \lbrace \pw.\sigma,
           \pb.\Lf{\length}{\mbox{1}}{\sigma}, \ldots\rbrace
                   ] \\
               \cal{P_{\mbox{\tiny \main}}} &=&
                   \lbrack~\pi_9 \mapsto \lbrace ep_4 \rbrace,  \
                    \pi_{10} \mapsto \lbrace ep_4 \rbrace,  \
                   \pi_{11} \mapsto \lbrace ep_4 \rbrace,  \pi_{12} \mapsto \lbrace ep_4 \rbrace~\rbrack
\end{eqnarray*}
    \end{minipage} \\
(a)&
(b)
    %% \end{ tabular}}
  \end{tabular}
%\end{picture}
\kern -3ex
%\vspace{0.5in}
\caption{(a) Example program and (b) its liveness
maps.}\label{fig:mot-example2}
\end{figure*}
%================================================================

@@

For  the  running  example,   $\length$  has  calls  from  $\main$  at
$\pi_{10}$ and a recursive call at $\pi_6$.
So $\sigma_{\length} =
     \deltacall{\length}{\pi_{11}}{\main}  \cup 
\deltacall{\length}{\pi_6}{\length}$.
Filling in  the values gives:
\begin{eqnarray*}
\sigma_{\length}    &=&
 \sigma_{\!all}  ~\cup~{\cbar\sigma_{\mathit{\length}}}
\end{eqnarray*}
As examples, the liveness of \Lanv{1}{\pl} and \Lanv{9}{\pb} in terms
of  $\sigma_{\length}$ are:
\begin{align*}
\Lanv{1}{\pl} &= \cbar\sigma_{\length} \cup \acdr\Df{\length}{1}\cbar\sigma_{\length}
  \cup \cbar\Df{\length}{1}{\cbar\sigma_{\length}}
 \\
\Lanv{9}{\pb} &= \Df{\length}{1}\sigma_{\mathit{\!all}}
\end{align*}

In summary, the equations generated during liveness analysis are:
\begin{enumerate}
\item   For    each   function   $\mathit{f}$,    equations   defining
\Df{f}{i} for use by \Lfonly$_{\mathit f}$.
\item  For  each   function  $\mathit{f}$, an  equation  defining
the summary demand  $\sigma_{\mathit f}$ on $e_f$.
\item For each function $\mathit{f}$ (including $\mainpgm$ for
  $e_\mainpgm$) 
an equation defining
  liveness at each GC point of $e_{\mathit f}$.
\end{enumerate}
\subsection{Solving liveness equations---the grammar
interpretation}\label{sec:grammar-formulation}
The  equations above can now be re-interpreted as a
context-free grammar (CFG)  on the alphabet $\lbrace\acar, \acdr,
\bcar, \bcdr, \cbar\rbrace$.  Let  \var{$X$} denote the non-terminal
for
a variable  $X$ occurring on  the LHS of the  equations generated
from the analysis.  We can  think of the resulting productions as
being associated with several  grammars, one for each non-terminal
\var{\Lanv{i}{x}} regarded as a start symbol.  As an example, the
grammar    for   \var{\Lanv{1}{\xl}}   comprises    the   following
productions:
 \begin{eqnarray*}
\var{\Lanv{1}{\xl}}  &\rightarrow&   \cbar\sigma_{\length} \mid \acdr \var{\Df
  {\length}{1}}{\cbar\sigma_{\length}} \mid
  \cbar\var{\Df{\length}{1}}{\cbar\sigma_{\length}} \\
  \var{\Df{\length}{1}} &\rightarrow& \cbar \mid
  \acdr\var{\Df{\length}{1}}\cbar 
       \mid \cbar\var{\Df{\length}{1}}{\cbar}\\
\langle {\sigma_{\length}} \rangle
&\rightarrow&
\sigma_{\!all}  \mid \cbar\langle{\sigma_{\length}}\rangle
\end{eqnarray*}
Other equations can be converted similarly.  The language generated by
\var{\Lanv{i}{x}},  denoted $\mathscr{L}(\var{\Lanv{i}{x}}) $,  is the
desired  solution of  \Lanv{i}{x}.  However,  recall from  our earlier
discussion that the decision problem  that we are interested in during
garbage collection at a program point $\pi_i$ is:
\begin{quote}
Let  $x.\alpha$ be  a forward  access  path consisting  only of  edges
\acar\    and   \acdr\    (but    not   \bcar, \bcdr\ or \cbar).     Let
$\mathscr{L}(\var{\Lanv{i}{x}}) \stackrel{*}{\hookrightarrow} \sigma$,
where $\sigma$ consists  of forward paths only. Then  does $\alpha \in
\sigma$?
\end{quote}

@@

\begin{figure*}[t]
\begin{boxedminipage}{.5\textwidth}
\begin{center}
  \raggedright  {\bf  Input:}  NFA \ntbar\  with  underlying
  alphabet $\lbrace \acar, \acdr, \bcar, \bcdr\rbrace$ \\
%
  \raggedright{\bf Output:} NFA  \nt\ with  underlying
  alphabet $\lbrace \acar, \acdr \rbrace$ such that
  $\lang{\ntbar} \stackrel{*}{\hookrightarrow} \lang{\nt}$.
  \\

  \raggedright{\bf Steps:}
 \begin{algorithmic}
   \STATE $i \leftarrow 0$
   \STATE $\nt_0 \leftarrow$ Equivalent NFA of \ntbar\
   without $\epsilon$-moves \cite{hopcraft90toc}

   \REPEAT
   \STATE $\nt'_{i+1} \leftarrow \nt_i$
   \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
     edge from $q'$ with label $\bcar$ and
     outgoing edge to $q''$ with label $\acar$}
   \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
   label $\epsilon$.
   \COMMENT{bypass  $\bcar\acar$ using $\epsilon$}
   \ENDFOR

   \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
     edge from $q'$ with label $\bcdr$ and outgoing edge to
     $q''$ with label $\acdr$}
   \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
     label $\epsilon$.
   \COMMENT{bypass  $\bcdr\acdr$ using $\epsilon$}
   \ENDFOR

   \STATE   $\nt_{i+1}    \leftarrow$   Equivalent   NFA   of
   $\nt'_{i+1}$ without $\epsilon$-moves

   \STATE $i \leftarrow i+1$
   \UNTIL ($\nt_{i} = \nt_{i-1}$)

   \STATE $\nt \leftarrow \nt_i$
  \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
 \end{algorithmic}
\end{center}
\end{boxedminipage}
\begin{boxedminipage}{.5\textwidth}
The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th

>>>>

\begin{figure*}[t!]
  \begin{tabular}{cc}
    \begin{minipage}{.40\textwidth}
        \small
        \renewcommand{\arraystretch}{1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\
(\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF\
$\psi_1\!\!:\,$ \px
            \UNL{4} \hspace*{.27cm} $\pi_3\!\!:\,
            $(\LET\ \pv\ $\leftarrow 0$ \IN
            \UNL{5} \hspace*{.32cm} $\pi_4\!\!:\,
(\SRETURN~\psi_2:\pv)$
            \UNL{4} \hspace*{.29cm}    $\pi_5\!\!:\, $(\LET~\pu\
$\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{.34cm}   $\pi_6\!\!:\, $(\LET~\py\
$\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{.34cm} $\pi_7\!\!:\,
            $(\LET~\pz\ $\leftarrow$ (1~+~\py) \IN
            \UNL{7} \hspace*{.34cm} $\pi_8\!\!:\,
(\SRETURN~\psi_3:\pz)$)))))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
	  \UNL{1} $(\DEFINE\ (\main)$ 
           \UNL{2} \!\!$\pi_9\!\!:\, \cred{(\LET\  \pa\  \leftarrow (\abigfunction\ \acdr)}$ \IN
          \UNL{3} \!\!$\pi_{10}\!\!:\, \cred{(\LET\  \pb\  \leftarrow (}$\cred{+}$\cred{\ \pa\ \acdr)}$
\IN
	  \UNL{4}   \hspace*{.05cm}$\pi_{11}\!\!:\,      $ \cred{(\LET\ \pc}\
$\cred{\leftarrow  (\CONS\ \pb\ ())}$ \IN
          \UNL{5}   \hspace*{.15cm}    $\pi_{12}\!\!:\,
          $\cred{(\LET\ \pw}\  $\cred{\leftarrow  (\length\ \pc)}$ \IN
          \UNL{6}  \hspace*{.25cm}  $\pi_{13}\!\!:\,
(\SRETURN~\psi_4:\pw)))))$
\end{uprogram}}
        %%}
    \end{minipage}

@@

        \small
\begin{eqnarray*}
        \mathcal{L}(e_{\length},\sigma,\Lfonly) &=&
              [\;ep_1 \mapsto \lbrace \px.\cbar \sigma,
\xl.\cbar\sigma\rbrace ,~ep_2 \mapsto \lbrace \cred{
\pv.\sigma}  \rbrace,\\
 &&          \;\;  ep_3 \mapsto \lbrace \pz.\sigma,
                \py.\cbar\sigma,
\pu.\Lf{\length}{\mbox{1}}{\cbar\sigma},\\
&&            \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\; 
\xl.\{ \acdr\Lf{\length}{\mbox{1}}{\cbar\sigma} \cup 
%%\;\;\;\;\;\;\; \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\\
\cred{\cbar\Lf{\length}{1}{\cbar\sigma}}\}\}
             \rbrack \\
            \cal{P_{\mbox{\tiny \length}}} &=&
                [\;\pi_1 \mapsto \lbrace ep_1, ep_2, ep_3 \rbrace,  \
                 \pi_2 \mapsto \lbrace ep_1, ep_2, ep_3
                  \rbrace, \\
&&\;\;  \pi_3 \mapsto \lbrace ep_2
                  \rbrace ,  \pi_4 \mapsto \lbrace ep_2
                  \rbrace, \pi_5 \mapsto \lbrace  ep_3 \rbrace, \\
 &&  \;\;                        \pi_6 \mapsto \lbrace ep_3 \rbrace,
\pi_7 \mapsto
                   \lbrace ep_3\rbrace, \pi_8 \mapsto \lbrace ep_3
\rbrace~\rbrack\\
              \mathcal{L}(e_{\main},\sigma,\Lfonly) &=&
                [\;
                  ep_4 \mapsto \lbrace \cred {\pw.\sigma,
                                       \pc.\Lf{\length}{\mbox{1}}{\sigma},}\\
&& \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
                                        \cred{\pb.\bcar\Lf{\length}{\mbox{1}}{\sigma},}
                                        \cred{\pa.\cbar\bcar\Lf{\length}{\mbox{1}}{\sigma}} \rbrace
                               ] \\
               \cal{P_{\mbox{\tiny \main}}} &=&
                  \lbrack~ \cred{\pi_9 \mapsto \lbrace ep_4 \rbrace,  \
                    \pi_{10} \mapsto \lbrace ep_4 \rbrace,  \
                   \pi_{11} \mapsto \lbrace ep_4 \rbrace,} \\
                   && \;\; \cred{\pi_{12} \mapsto \lbrace ep_4 \rbrace, \pi_{13} \mapsto \lbrace ep_4 \rbrace}~\rbrack
\end{eqnarray*}
    \end{minipage} \\
(a)&
(b)
    %% \end{ tabular}}
  \end{tabular}
%\end{picture}
\kern -3ex
%\vspace{0.5in}
\caption{(a) Example program and (b) its liveness
maps.}\label{fig:mot-example2}
\end{figure*}
%================================================================

@@

For  the  running  example,   $\length$  has  calls  from  $\main$  at
$\pi_{12}$ and a recursive call at $\pi_6$.
So $\sigma_{\length} =
     \deltacall{\length}{\pi_{12}}{\main}  \cup 
\deltacall{\length}{\pi_6}{\length}$.
Filling in  the values gives:
\begin{eqnarray*}
\sigma_{\length}    &=&
 \sigma_{\!all}  ~\cup~{\cbar\sigma_{\mathit{\length}}}
\end{eqnarray*}
As examples, the liveness of \Lanv{1}{\pl} and \Lanv{9}{\pc} in terms
of  $\sigma_{\length}$ are:
\begin{align*}
\Lanv{1}{\pl} &= \cbar\sigma_{\length} \cup \acdr\Df{\length}{1}\cbar\sigma_{\length}
  \cup \cbar\Df{\length}{1}{\cbar\sigma_{\length}}
 \\
\Lanv{9}{\pc} &= \Df{\length}{1}\sigma_{\mathit{\!all}}
\end{align*}

In summary, the equations generated during liveness analysis are:
\begin{enumerate}
\item   For    each   function   $\mathit{f}$,    equations   defining
\Df{f}{i} for use by \Lfonly$_{\mathit f}$.
\item  For  each   function  $\mathit{f}$, an  equation  defining
the summary demand  $\sigma_{\mathit f}$ on $e_f$.
\item For each function $\mathit{f}$ (including $\mainpgm$ for
  $e_\mainpgm$) 
an equation defining
  liveness at each GC point of $e_{\mathit f}$.
\end{enumerate}
\subsection{Solving liveness equations---the grammar
interpretation}\label{sec:grammar-formulation}
The  equations above can now be re-interpreted as a
context-free grammar (CFG)  on the alphabet $\lbrace\acar, \acdr,
\bcar, \bcdr, \cbar\rbrace$.  Let  \var{$X$} denote the non-terminal
for
a variable  $X$ occurring on  the LHS of the  equations generated
from the analysis.  We can  think of the resulting productions as
being associated with several  grammars, one for each non-terminal
\var{\Lanv{i}{x}} regarded as a start symbol.  As an example, the
grammar    for   \var{\Lanv{1}{\xl}}   comprises    the   following
productions:
 \begin{eqnarray*}
\var{\Lanv{1}{\xl}}  &\rightarrow&   \cbar\sigma_{\length} \mid \acdr \var{\Df
  {\length}{1}}{\cbar\sigma_{\length}} \mid
  \cbar\var{\Df{\length}{1}}{\cbar\sigma_{\length}} \\
  \var{\Df{\length}{1}} &\rightarrow& \cbar \mid
  \acdr\var{\Df{\length}{1}}\cbar 
       \mid \cbar\var{\Df{\length}{1}}{\cbar}\\
\langle {\sigma_{\length}} \rangle
&\rightarrow&
\cred{\epsilon}  \mid \cbar\langle{\sigma_{\length}}\rangle
\end{eqnarray*}
Other equations can be converted similarly.  The language generated by
\var{\Lanv{i}{x}},  denoted $\mathscr{L}(\var{\Lanv{i}{x}}) $,  is the
desired  solution of  \Lanv{i}{x}.  However,  recall from  our earlier
discussion that the decision problem  that we are interested in during
garbage collection at a program point $\pi_i$ is:
\begin{quote}
Let  $x.\alpha$ be  a forward  access  path consisting  only of  edges
\acar\    and   \acdr\    (but    not   \bcar, \bcdr\ or \cbar).     Let
$\mathscr{L}(\var{\Lanv{i}{x}}) \stackrel{*}{\hookrightarrow} \sigma$,
where $\sigma$ consists  of forward paths only. Then  does $\alpha \in
\sigma$?
\end{quote}

@@

\begin{figure*}[t]
%% \begin{boxedminipage}{.5\textwidth}
%% \begin{center}
%%   \raggedright  {\bf  Input:}  NFA \ntbar\  with  underlying
%%   alphabet $\lbrace \acar, \acdr, \bcar, \bcdr\rbrace$ \\
%% %
%%   \raggedright{\bf Output:} NFA  \nt\ with  underlying
%%   alphabet $\lbrace \acar, \acdr \rbrace$ such that
%%   $\lang{\ntbar} \stackrel{*}{\hookrightarrow} \lang{\nt}$.
%%   \\

%%   \raggedright{\bf Steps:}
%%  \begin{algorithmic}
%%    \STATE $i \leftarrow 0$
%%    \STATE $\nt_0 \leftarrow$ Equivalent NFA of \ntbar\
%%    without $\epsilon$-moves \cite{hopcraft90toc}

%%    \REPEAT
%%    \STATE $\nt'_{i+1} \leftarrow \nt_i$
%%    \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
%%      edge from $q'$ with label $\bcar$ and
%%      outgoing edge to $q''$ with label $\acar$}
%%    \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
%%    label $\epsilon$.
%%    \COMMENT{bypass  $\bcar\acar$ using $\epsilon$}
%%    \ENDFOR

%%    \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
%%      edge from $q'$ with label $\bcdr$ and outgoing edge to
%%      $q''$ with label $\acdr$}
%%    \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
%%      label $\epsilon$.
%%    \COMMENT{bypass  $\bcdr\acdr$ using $\epsilon$}
%%    \ENDFOR

%%    \STATE   $\nt_{i+1}    \leftarrow$   Equivalent   NFA   of
%%    $\nt'_{i+1}$ without $\epsilon$-moves

%%    \STATE $i \leftarrow i+1$
%%    \UNTIL ($\nt_{i} = \nt_{i-1}$)

%%    \STATE $\nt \leftarrow \nt_i$
%%   \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
%%  \end{algorithmic}
%% \end{center}
%% \end{boxedminipage}
\begin{boxedminipage}{.5\textwidth}
The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th The algorithm repeatedly introduces  $\epsilon$ edges to bypass a pair
of consecutive edges labelled  \bcar\acar\ or \bcdr\acdr.  The process
is continued till  a fixed point is reached.  When  the fixed point is
reached,   the  resulting   NFA  contains   all   possible  reductions
corresponding to all the paths in the original NFA.  The proofs of the
termination and correctness  of th
